%----------------------------------------------------------------------------------------
%    DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------
\documentclass[a4paper,10pt]{article}

%----------------------------------------------------------------------------------------
%    PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[left=1.0cm,top=1.0cm,right=1.0cm,bottom=1.0cm]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[unicode, draft=false]{hyperref}

%----------------------------------------------------------------------------------------
%    CONFIGURATIONS
%----------------------------------------------------------------------------------------
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}

% Custom \section formatting
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{14pt}{10pt}

% Link Colors
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

% SHORT job entry: Title | Date
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill & \small #2 \\[3pt]
    \end{tabularx}
    }
    {}

% LONG job entry: Title | Tech Stack | Bullets
\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill & \textit{\small #2} \\[3pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut,leftmargin=1em,itemsep=3pt,label=\textbullet]
    }
    {
    \end{itemize}
    \end{minipage}\vspace{8pt}
    }

%----------------------------------------------------------------------------------------
%    BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty}

%----------------------------------------------------------------------------------------
%    HEADER
%----------------------------------------------------------------------------------------
\begin{center}
    {\LARGE \scshape Gonzalo Cruz Gómez} \\ \vspace{3pt}
    \small
    \href{mailto:gonza.c.gomez03@gmail.com}{gonza.c.gomez03@gmail.com} $|$
    \href{https://github.com/gonzalo-cruz}{github.com/gonzalo-cruz} $|$
    \href{https://gonzalo-cruz.vercel.app/}{gonzalo-cruz.vercel.app}
\end{center}

\vspace{6pt}
{\small Data Science \& Engineering undergraduate (3rd year, URJC) with a background in Telecommunications Engineering. Builds production-ready data systems: end-to-end ML pipelines, distributed computing, and deep learning. Founder of Asociación Datalab. Seeking an internship in data science or data engineering.}

%----------------------------------------------------------------------------------------
%    EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X r@{}}
\textbf{B.S. Data Science \& Engineering} & \textbf{URJC} & \textit{2024 -- Present} \\
\multicolumn{3}{@{}l@{}}{\small \quad $\bullet$ Completed two academic years in one (2024--2025). Coursework: ML, Distributed Systems, Deep Learning, HPC.} \\[5pt]
\textbf{B.S. Telecommunications Engineering} & \textbf{UC3M} & \textit{2019 -- 2023} \\
\multicolumn{3}{@{}l@{}}{\small \quad $\bullet$ 120+ credits in Networking, Physics and Signal Processing. Transferred to specialize in Data Science.} \\[5pt]
\textbf{Certificate of Advanced English (C2)} & Cambridge Assessment & \textit{2019}
\end{tabularx}

%----------------------------------------------------------------------------------------
%    PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}

\begin{joblong}{TripAdvisor Restaurants Data Pipeline}{Python, Apache Airflow, Kafka, Scikit-learn, Pandas}
\item Orchestrated a 5-task ETL pipeline with Apache Airflow, processing \textbf{1M+ rows} in 50k-row chunks to stay memory-safe throughout — extract, clean, EDA, preprocessing, and load.
\item Fitted \texttt{IncrementalPCA} and \texttt{StandardScaler} via \texttt{partial\_fit} on batches; applied OHE or label encoding per column based on cardinality.
\item Streamed the processed dataset to Kafka using a fault-tolerant producer (\texttt{acks=all}, sub-batch delivery) ready for downstream consumption.
\item Centralised all pipeline parameters (chunk size, thresholds, Kafka config) in a single \texttt{config.toml}; all tasks read from it at runtime.
\end{joblong}

\begin{joblong}{Forest Fire Spread Prediction}{R, GLMs, GAMs, Statistical Modeling}
\item Built GLM and GAM regression models to predict fire-burned area from meteorological covariates; GAMs outperformed GLMs on held-out data with lower residual variance.
\item Resolved severe data quality issues (high skew, missing values, near-zero-variance predictors) via log transformation, imputation, and feature selection.
\item Applied cross-validation to compare model fits; selected GAMs as the final model based on lower RMSE and better capture of non-linear covariate effects.
\end{joblong}

\begin{joblong}{Stroke Risk Classification}{Python, Scikit-learn, TensorFlow, ANN}
\item Trained an MLP on an imbalanced medical dataset, applying SMOTE and optimizing the decision threshold to minimize false negatives given the clinical cost of missed strokes.
\item Selected AUC-ROC and F1 as evaluation metrics over accuracy; tuned architecture and hyperparameters accordingly.
\item Benchmarked the MLP against a logistic regression baseline; the non-linear model improved recall on the stroke class while maintaining acceptable precision.
\end{joblong}

%----------------------------------------------------------------------------------------
%    EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Experience}

\begin{jobshort}{Founder \& President --- Asociación Datalab}{May 2025 -- Present}
\small Established the university's first Data Science student association: defined the strategic roadmap, handled legal registration, and organized technical workshops.
\end{jobshort}

\vspace{10pt}
\begin{jobshort}{Private Tutor --- Mathematics \& Physics}{Sep 2021 -- Present}
\small Mentored high-school students over 5 years, achieving a \textbf{100\% pass rate} and helping 90\% of students improve by at least 3 grade points through personalized plans.
\end{jobshort}

%----------------------------------------------------------------------------------------
%    SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Programming:}  & Python (Advanced), R, SQL, C \\
\textbf{Data Science:} & Scikit-learn, PyTorch, TensorFlow, Pandas, NumPy, Hadoop, Spark, Matplotlib \\
\textbf{Engineering:}  & Apache Airflow, Kafka, Docker, Git/GitHub, Linux (Bash) \\
\textbf{HPC:}          & OpenMP, MPI, CUDA \\
\textbf{Languages:}    & Spanish (Native), English (C2), German (B1), Chinese (HSK3) \\
\end{tabularx}

\end{document}
